Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-04-10 pkg/circtree/inst/wind_paper/draft/draft_submitted_2020_01_09.tex
Update make diff for draft.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3007 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 735d1b2c68023e00f6d83f0584a7386adb699856

\section*{Computational details}
The corresponding implementation of the proposed methodology for circular
regression trees and forests is provided in the \textsf{R} package
\textbf{circtree} (version~\Sexpr{packageVersion("circtree")}). The package is
based on the \textbf{disttree} package
(version~\Sexpr{packageVersion("disttree")}) which applies the main tree
building functions from the \textbf{partykit} package
(version~\Sexpr{packageVersion("partykit")}). All three packages are available
on \textsf{R}-Forge at {\url{https://R-Forge.R-project.org/projects/partykit/}}.

>>>>

\section*{Computational details}
The corresponding implementation of the proposed methodology for circular
regression trees and forests is provided in the \textsf{R} package
\textbf{circtree} (version~0.1.0). The package is
based on the \textbf{disttree} package
(version~0.2.0) which applies the main tree
building functions from the \textbf{partykit} package
(version~1.2.7). All three packages are available
on \textsf{R}-Forge at {\url{https://R-Forge.R-project.org/projects/partykit/}}.
